---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<style type="text/css">
  body {
    font-family: 'Montserrat', sans-serif;
    font-weight: 500;
    font-size: 16px;
    color: #545859;
  }
</style>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Quick Start

<!-- badges: start -->

<!-- badges: end -->

Handwriter is designed to assist forensic examiners by analyzing handwritten documents against a closed set of potential writers. It determines the probability that each writer wrote the document. Whether you are a forensic document examiner, legal professional, academic, or simply curious about how statistics are applied to handwriting, handwriter provides an automated way to evaluate handwriting samples.

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub.
